Title

### 2013-03-31 TCAD2013/overclocking_tcad.tex
Describe tradeoffs

%% bare_jrnl.tex
%% V1.4
%% 2012/12/27
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8 or later) with an IEEE journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex,
%%                    bare_jrnl_transmag.tex
%%*************************************************************************

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

@@

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

@@

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Title}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~11, No.~4, December~2012}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2012 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

@@

\subsection{Model Verification}
As seen in (\ref{CSA_Timing}), the value of $\mu_{mux}/\mu_c$ should be determined before applying the timing model. This is achieved by keeping $i=0$ in (\ref{CSA_SingleStageDelay}) while varying the value of $n_0$. The corresponding $d_0$ is recorded through the timing analysis tool. Hence $\mu_{mux}/\mu_c$ can be obtained by fitting those values, as presented in Figure.xxx. Out experimental results show that $\mu_{mux}/\mu_c\approx8$.

@@

\subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
Although advanced architectures such as CSA inheritly offer better performance than the basic structure, this would generate a large area overhead. In the following experiments, the trade-offs between accuracy, performance as well as area are explored. If the available hardware resources are limited, the full word-length of both CSA and RCA might not be implemented. Therefore truncation errors would be generated. For instance, the number of available LUTs is set to 45, 35, 25 and 15 respectively. The corresponding error expectations of RCA and CSA are demonstrated in Fig.xxx. The optimal design method which achieves the minimum error expectation is labelled.
\begin{figure}[htbp]
	\centering
	\includegraphics[width=3.3in]{./Figures/Error_LUT45.eps}
	\caption{LUT=45}
\end{figure}

@@

%\begin{figure*}[htbp]
%  \centering
%  \subfigure[LUTs=45]{
%  \begin{minipage}[c]{0.45\textwidth}
%    \centering
%    \includegraphics[width=2in]{./Figures/Error_LUT45.eps}
%  \end{minipage}%
%  }%
%  \subfigure[LUT=35]{
%  \begin{minipage}[c]{0.45\textwidth}
%    \centering
%    \includegraphics[width=2in]{./Figures/Error_LUT35.eps}
%  \end{minipage}
%  }
%  \subfigure[LUT=25]{
%  \begin{minipage}[c]{0.45\textwidth}
%    \centering
%    \includegraphics[width=2in]{./Figures/Error_LUT25.eps}
%  \end{minipage}
%  }%
%  \subfigure[LUT=15]{
%  \begin{minipage}[c]{0.45\textwidth}
%    \centering
%    \includegraphics[width=2in]{./Figures/Error_LUT15.eps}
%  \end{minipage}
%  }
%  \caption{Accuracy-performance trade-offs under fixed area constraints.}
%  \label{Fig Tradeoffs}
%\end{figure*}
%the maximum word-lengths of RCA and CSA under given area constraints are listed in Table.xxx

It can be seen that if area is not limited, CSA with higher stage numbers serve as the optimal design choice for most frequency values, as we discussed in Section.xxx. While overclocking the RCA achieves better accuracy at higher frequencies, d
%According to

@@

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

%\appendices
%\section{Proof of the First Zonklar Equation}
%Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
%\section{}
%Appendix two text goes here.

>>>>

%% bare_jrnl.tex
%% V1.4
%% 2012/12/27
%% by Michael Shell

\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

@@

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}

@@

\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

\title{Title}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~11, No.~4, December~2012}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}

@@

\subsection{Model Verification}
As seen in (\ref{CSA_Timing}), the value of $\mu_{mux}/\mu_c$ should be determined before applying the timing model. This is achieved by keeping $i=0$ in (\ref{CSA_SingleStageDelay}) while varying the value of $n_0$. The corresponding $d_0$ is recorded through the timing analysis tool. Hence $\mu_{mux}/\mu_c$ can be obtained by fitting those values, as presented in Fig.~(\ref{DelayFitting}). Out experimental results show that $\mu_{mux}/\mu_c\approx8$.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=3.3in]{./Figures/Fitting.eps}
  \caption{Fitted curve of (\ref{CSA_SingleStageDelay}) for the most significant stage ($i=0$), based on the delay value obtained through the Xilinx Timing Analyzer.}
  \label{DelayFitting}
\end{figure}

@@

\subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
Although advanced architectures such as CSA inheritly offer better performance than the basic structure, this would generate a large area overhead. In the following experiments, the trade-offs between accuracy, performance as well as area are explored. If the available hardware resources are limited, the full word-length of both CSA and RCA might not be implemented. This potentially generate truncation errors. For instance, the number of available LUTs is set to 45, 35, 25 and 15 respectively, while timing requirements are met by reducing the input word-length of each architecture. In addition, we also investigate the scenario where RCA is implemented with the maximum possible word-length under the given area constraint, while meeting timing by overclocking. The corresponding error expectations of these scenarios are depicted in Fig.xxx. The optimal design method which achieves the minimum error expectation is labelled.
\begin{figure}[htbp]
	\centering
	\includegraphics[width=3.3in]{./Figures/Error_LUT45.eps}
	\caption{LUT=45}
\end{figure}

@@

%\begin{figure*}[htbp]
%  \centering
%  \subfigure[LUTs=45]{
%  \begin{minipage}[c]{0.45\textwidth}
%    \centering
%    \includegraphics[width=2in]{./Figures/Error_LUT45.eps}
%  \end{minipage}%
%  }%
%  \subfigure[LUT=35]{
%  \begin{minipage}[c]{0.45\textwidth}
%    \centering
%    \includegraphics[width=2in]{./Figures/Error_LUT35.eps}
%  \end{minipage}
%  }
%  \subfigure[LUT=25]{
%  \begin{minipage}[c]{0.45\textwidth}
%    \centering
%    \includegraphics[width=2in]{./Figures/Error_LUT25.eps}
%  \end{minipage}
%  }%
%  \subfigure[LUT=15]{
%  \begin{minipage}[c]{0.45\textwidth}
%    \centering
%    \includegraphics[width=2in]{./Figures/Error_LUT15.eps}
%  \end{minipage}
%  }
%  \caption{Accuracy-performance trade-offs under fixed area constraints.}
%  \label{Fig Tradeoffs}
%\end{figure*}

If there is no area limitation, CSA with higher stage numbers will be the optimal design choice unless very high frequencies are applied. This is because a long carry chain is divided into multiple overlapped sections in comparison to RCA, and the higher stage number the shorter the carry chain length of each stage. When the frequency increases, however, the multiplexer delay becomes comparable to the carry chain delay, and this will limit the maximum word-length of CSA. It can be seen that the overclocked RCA outperforms at higher frequencies.

For a tighter area budget, only part of the complex structures can be implemented, while the simple structure still keep full precision. As can be seen in Fig.xxx and Fig.xxx, area instead of timing becomes dominate when the frequency is initially increased. This lead to the truncation of word-length of both 2-stage and 3-stage CSA. For an even stringent area constraint, the word-length of RCA is limited, meanwhile CSA with high stage numbers could not be implemented, as shown in Fig.xxx. In this situation the overclocked RCA achieves best accuracy across the whole frequency domain.

In general, the error expectations at the output of all four design method for a variety of timing and area constraints are demonstrated in Fig.~\ref{Tradeoff}.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=3.3in]{./Figures/Tradeoff.eps}
  \caption{Trade-offs between accuracy, performance and area for 4 design methodologies.}
  \label{Tradeoff}
\end{figure}

@@
